A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-07-01 paper/paper.Rnw
More tweaks to header/author statements

%% Group authors per affiliation:
% \author{Miranda Tilton and Susan Vanderplas\fnref{csafe}}
% \address{Iowa State University Statistics Department}
% \fntext[csafe]{195 Durham Center, 613 Morill Rd., Ames, IA 50011}

% or include affiliations in footnotes:
\author[1]{Miranda Tilton and Susan Vanderplas\corref{cor1}\fnref{isu}}
\cortext[cor1]{Corresponding author}
\ead{srvander@iastate.edu}

\address[1]{195 Durham Center, 613 Morill Rd, Ames, IA 50011}
\fntext[isu]{Center for Statistical Applications in Forensic Evidence, Iowa State University}

>>>>

%% Group authors per affiliation:
\author{Miranda Tilton and Susan Vanderplas\fnref{csafe}}
\address{Center for Statistical Applications in Forensic Evidence, Iowa State University}
\fntext[csafe]{195 Durham Center, 613 Morill Rd., Ames, IA 50011.}

% or include affiliations in footnotes:
% \author[1]{Miranda Tilton and Susan Vanderplas\corref{cor1}\fnref{isu}}
% \cortext[cor1]{Corresponding author}
% \ead{srvander@iastate.edu}
%
% \address[1]{195 Durham Center, 613 Morill Rd, Ames, IA 50011}
% \fntext[isu]{Center for Statistical Applications in Forensic Evidence, Iowa State University}
